Rule Synthesis for Rule-based Intrusion Detectors

### 2020-06-02 paper/paper.tex
polishing

RQ1 assesses \tname's performance. The metric we use is the position
of the golden rule at the ranked list of plausible rules reported by
\tname\ (see Figure~\ref{fig:overview}). This metric is a proxy of
human performance in analyzing the list of plausible rules.

@@

Table~\ref{table:results} shows results. Column ``Name'' shows the
name of the attack, column ``\#~Vars.'' shows the number of variants
of the attack, column ``\#~Option Cand. (step~1)'' shows the number of
option candidates reported by \tname\ at step 1, column ``\#~Plausible
Rules (step~2)'' shows the number of rules reported by \tname\ at step
2, and column ``Rank (step~3)'' shows the position of the golden rule
in the reported ranking. Observe that the number of option candidates
is considerably higher for attacks captured with content options
compared to attacks not involving content options. This happens
because for content attacks the number of option candidates depend on
the unbounded size of the http payload whereas for attacks of
different protocols the number of option candidates depend on the
layout of the messages. Also observe that the number of plausible
rules is much smaller for non-content attacks compared to content
attacks.

>>>>

RQ1 assesses \tname's performance. The metric we use is the position
of the golden rule in the ranked list of plausible rules reported by
\tname\ (see Figure~\ref{fig:overview}). This metric is a proxy of
human performance in analyzing the list of plausible rules.

@@

Table~\ref{table:results} shows the results, where ``Name'' is 
name of the attack, ``\#~Vars.'' is the number of variants
of the attack, ``\#~Option Cand. (step~1)'' is the number of
option candidates reported by \tname\ at step 1, ``\#~Plausible
Rules (step~2)'' is the number of rules reported by \tname\ at step
2, and  ``Rank (step~3)'' is the position of the golden rule
in the reported ranking. Observe that the number of option candidates
is considerably higher for attacks captured with content options
compared to attacks not involving content options. This happens
because for content attacks the number of option candidates depend on
the unbounded size of the http payload whereas for attacks of
different protocols the number of option candidates depend on the
layout of the messages. Also observe that the number of plausible
rules is much smaller for non-content attacks compared to content
attacks.
